---
title: "R - QUIZ"
author: "`r paste(params$Name, params$Surname, params$StudentID)`"
date: '`r format(Sys.time(), "%d/%m/%Y, %H:%M:%S")`'
output: html_document
linkcolor: black
geometry: margin = 1.05in
fontsize: 12pt
params:
  Name: NA
  Surname: NA
  StudentID: NA
  Question1_code: NA
  Question2_code: NA
  Question3_code: NA
---

```{r include = FALSE}
#knitr::opts_chunk$set(echo=FALSE,results='hide',fig.show = 'hide')
```

# Question 1:

Write an R function that takes a vector of real numbers and returns minimum, average and sum of the elements respectively as a vector object.

```{r echo=FALSE, eval=FALSE, results=FALSE}
Oltulu_Q1 <- function(x){
  return(c(minimum = min(x),
           average = mean(x), 
           sum = sum(x)))
}
```

**Question 1 Code:**

```{r}
# Your code in characters: 
params$Question1_code
```

**Your code:** 

`r params$Question1_code`

&nbsp; 


# Question 2:

Write an R function that that given a vector of real numbers and an integer, will return how many times the integer appears inside the vector.

```{r echo=FALSE, eval=FALSE, results=FALSE}
Oltulu_Q2 <- function(x,y){
  return(sum(x==y))
}
```


**Question 2 Code:**

```{r}
# Your code in characters: 
params$Question2_code
```

**Your code:** 

`r params$Question2_code`

&nbsp; 


# Question 3:

Write an R function that takes a vector of values and returns a line graph. You have to add a custom title, y-axis label, and color to your plot.

```{r echo=FALSE, eval=FALSE, results=FALSE}
Oltulu_Q3 <- function(a){
  return(plot(a, main = "Q3 plot", type = "l", col = "Blue", ylab = "y"))
}
```

**Question 3 Code:**

```{r}
# Your code in characters: 
params$Question3_code
```

**Your code:** 

`r params$Question3_code`

&nbsp; 



